Bayesian Sparsification of $\cplx$-valued networks

### 2020-01-29 paper/paper.tex
stub version of the experimental section

>>>>

% general training strategy
The goal of the following experiments to study the sparsity-performance trade-off of the
proposed Bayesian sparsification methods for $\cplx$-valued networks. To this end we employ
the following training plan in every experiment. The model is trained in three successive
stages:
``dense'' $\to$ ``sparsify'' $\to$ ``fine-tune''

At the first, ``dense'', stage every network retains its original non-bayesian layers
and is fit ``as-is'' using only the likelihood from \eqref{eq:elbo} without variational
dropout.

During the second stage ``sparsify'' we make the relevant layers bayesian and apply
variational dropout sec.~\ref{ssub:variational_dropout} (or sec.~\ref{ssub:empirical_bayes})
or their $\real$ counterparts. To be able to study the attainable sparsity levels we
inject a coefficient $C \in (0, 1]$ at the KL divergence term in
\eqref{eq:elbo}:
\begin{equation}  \label{eq:elbo_with_coef}
    - \frac{C}N KL(q_{\theta} \| \pi_{\lambda})
    + \frac1{M} \sum_{i=1}^M
        \log p_{\phi}(z_i \mid g(\varepsilon_i; \theta))
    \,. \tag{\ref{eq:elbo}'}
\end{equation}
Increasing $C$ yields increasingly more sparse networks upon termination of this stage.

Before transitioning to the ``fine-tune'' stage we compute the mask of non-zero weights
in each layer based on the relevance scores $\alpha$ (sec.~\ref{sub:dropout}). Since
the variational approximation factorizes into univariate distributions, whether a $\cplx$
or $\real$ parameter is zero or not is determined from its relevance score $
  \alpha = \tfrac{\sigma^2}{\lvert\mu\rvert^2}
$: non-zero (relevant) if $\log \alpha \leq \tau$, zero (irrelevant) otherwise.
In every experiment we set $\tau = -\tfrac12$, which yields extreme levels of sparsity,
especially considering that the recommended setting in \citep{molchanov_variational_2017}
was $3$. The rationale behind our choice was twofold: we use an extra fine tuning
stage, and keep the weights that are away from zero with high probability.

These masks are then used during ``fine-tune'' to train the remaining non-zero parameters
similar to the ``dense'' stage, i.e. with layers non-bayesian layers, but with fixed
sparsity masks.

Unless specified otherwise we use ADAM optimizer with the base learning rate of $10^{-3}$
and the annealing schedule from .

\subsection{MNIST-like datasets} % (fold)
\label{sub:mnist_like_datasets}

We conduct a moderately sized numerical experiment on MNIST and similar datasets to see
whether the proposed $\cplx$-var dropout indeed reasonably sparsifies complex-valued networks.

We compare with the studied $\cplx$-valued networks against their classical $\real$-valued
counterparts both in terms of the resulting sparsity and test performance.

Although image data is not $\cplx$ in nature, we apply two-dimensional Fourier Transform
in order to get $\cplx$-valued inputs. We concede that this is a rather unnatural representation
of image data, however the selection of publicly available datasets, which are not artificially
$\cplx$-valued, is limited to audio, speech and music. Indeed, as is shown by the numerical
experiments, a real-valued model is trained on the Fourier transformed data underperforms
relative to its architecturally similar twin fit to on the raw color data.

\citet{trabelsi_deep_2017} study the applicability of $\cplx$-valued networks to image
classification (CIFAR-10, CIFAR-100, and a subset of SVHN). Their approach is to either
embed $\real$ in $\cplx$ (by $\Re z = 0$), or train a smaller auxiliary network, that
synthesizes the imaginary component from the raw channel data. \todo{DO THIS}
In our experiments we opt to transforming the input $2d$ data with

% subsection mnist_like_datasets (end)
